\chapter{Conclusion} \label{chap:conclusion}

In this thesis, we have explored the application of nested simulation procedures in the risk management of financial derivatives and insurance products, with a particular focus on variable annuity contracts featuring \gls{gmmb} and \gls{gmwb}. 
Recognizing the computational challenges inherent in the standard nested simulation procedure, especially when estimating tail risk measures for complex financial products, we have proposed an innovative approach that integrates machine learning-based metamodels into the nested simulation framework.

We have shown that the nested simulation framework can be used to efficiently estimate risk measures of complex financial products, such as \gls{va}s, by combining machine learning-based metamodels with nested simulations.

Our primary contribution lies in the development and implementation of \gls{lstm}s as metamodels for the inner simulations within the nested simulation procedure. 
By employing \gls{lstm}s, we have effectively approximated the contract losses associated with dynamic hedging strategies under various market scenarios. 
This approach has substantially reduced the computational complexity of the standard nested simulation procedure while maintaining high levels of accuracy in risk estimation. 
The \gls{lstm} metamodels have captured the temporal dependencies and nonlinear relationships present in financial time series data, enabling efficient estimation of tail risk measures.

Through extensive numerical experiments and sensitivity analysis, we have demonstrated that our \gls{lstm}-based nested simulation procedure provides accurate and computationally efficient estimates of the tail risk associated with \gls{va} contracts. 
The results have shown that the metamodels can effectively replace the computationally intensive inner simulations in the standard nested simulation procedure.
This approachhas reduced the overall runtime without compromising the precision of risk assessments.
This efficiency gain is particularly valuable for insurers and financial institutions that require timely and accurate risk evaluations to meet regulatory requirements and make informed and timely risk management decisions.

Additionally, we have investigated the feasibility of our approach under changing market conditions and different \gls{va} contract features. 
By incorporating \gls{tl} techniques, we have enabled rapid adaptation of the \gls{lstm} metamodels to new contracts and evolving market dynamics. 
This aspect of our research highlights the potential for machine learning models to not only improve computational efficiency but also enhance the flexibility and responsiveness of risk management practices in the face of market volatility.

This thesis is an attempt to bridge the gap between traditional simulation schemes and modern machine learning techniques in the context of financial risk management.
By combining advanced machine learning techniques with financial risk management practices, this thesis contributes to the development of more efficient, adaptable, and robust methodologies that are essential in the rapidly evolving landscape of quantitative finance and actuarial science.